---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# XploRer

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)  
[![R build status](https://github.com/VEZY/XploRer/workflows/R-CMD-check/badge.svg)](https://github.com/VEZY/XploRer/actions)
<!-- badges: end -->

The goal of XploRer is to read, write, analyze and plot MTG (Multi-scale Tree Graph) files. These files describe the plant topology (i.e. structure) along with some attributes for each node (e.g. geometry, colors, state...). 

> The package is under intensive development and is in a very early version. The functions may heavily change from one version to another until a more stable version is released.

## Table of Contents

* [1. Installation](#1-installation)
* [2. Examples](#2-examples)
  * [2.1 Reading a file](#21-reading-a-file)
  * [2.2 Plot](#22-plotting-a-plant)
* [3. Help](#3-help)

## 1. Installation


you can install the release version of XploRer from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("VEZY/XploRer")
```

## 2. Examples

### 2.1 Reading a file

Read a simple MTG file:

```{r example}
library(XploRer)
MTG = read_MTG("https://raw.githubusercontent.com/VEZY/XploRer/master/inst/extdata/simple_plant.mtg")
```

The `read_MTG()` function returns a list of 4: 

- classes: a `data.frame` that holds information about the type of nodes used in the MTG (e.g. Internode, Leaf, etc...), the MTG scale for each one, and some more details. Here is the classes `data.frame` from our example:

    ```{r}
    MTG$classes
    ```

- description: a `data.frame` defining the potential topological constraints existing between nodes. Here is the description `data.frame` from our example:

    ```{r}
    MTG$description
    ```

- features: a `data.frame` listing all attributes present in the file and their associated type. Here is the features `data.frame` from our example:

    ```{r}
    MTG$features
    ```

- MTG: a `data.tree` strucuture defining all nodes, their attributes and their relationships:

    ```{r}
    MTG$MTG
    ```

### 2.2 Plotting a plant

The plant topology can be plotted using the `plot_MTG()` function:

```{r}
plot_MTG(MTG)
```

## 3. Help

Please see the [OpenAlea documentation](http://openalea.gforge.inria.fr/doc/vplants/newmtg/doc/_build/html/contents.html) (especially chapter 8) for more details on the MTG files. 

If you have any other problem related to the package, please feel free to [fill an issue](https://github.com/VEZY/XploRer/issues) on Github.
